Title Goes Here

### 2020-03-27 analysis/paper/paper.Rmd
tried ggfortify package

###I need to figure out how to group them

>>>>

#https://towardsdatascience.com/principal-component-analysis-pca-101-using-r-361f4c53a9ff <- another way of PCA, relationship with two variables

#using ggfortify package
library(ggfortify) 
autoplot(prcomp(DF))

###I need to figure out how to group them  -- by phase?
